---
title: "Final Project"
output: pdf_document
date: '2022-09-24'
---

```{r, echo=F}
fire_data <- read.csv("Fire Incidents Data.csv", header=T)
```

Remove the variables that are not studied
```{r, echo=F}
fire_data$Area_of_Origin <- NULL
fire_data$Building_Status <- NULL
fire_data$Business_Impact <- NULL
fire_data$Possible_Cause <- NULL
fire_data$Civilian_Casualties <- NULL
fire_data$Count_of_Persons_Rescued <- NULL
fire_data$Estimated_Dollar_Loss <- NULL
fire_data$Estimated_Number_Of_Persons_Displaced <- NULL
fire_data$Exposures <- NULL
fire_data$Ext_agent_app_or_defer_time <- NULL
fire_data$Final_Incident_Type <- NULL
fire_data$Fire_Alarm_System_Impact_on_Evacuation <- NULL
fire_data$Fire_Alarm_System_Presence <- NULL
fire_data$Incident_Number <- NULL
fire_data$Incident_Station_Area <- NULL
fire_data$Incident_Ward <- NULL
fire_data$Initial_CAD_Event_Type <- NULL
fire_data$Intersection <- NULL
fire_data$Last_TFS_Unit_Clear_Time <- NULL
fire_data$Latitude <- NULL
fire_data$Level_Of_Origin <- NULL
fire_data$Longitude <- NULL
fire_data$Material_First_Ignited <- NULL
fire_data$Method_Of_Fire_Control <- NULL
fire_data$Number_of_responding_apparatus <- NULL
fire_data$Property_Use <- NULL
fire_data$Smoke_Alarm_at_Fire_Origin <- NULL
fire_data$Smoke_Alarm_at_Fire_Origin_Alarm_Failure <- NULL
fire_data$Smoke_Alarm_at_Fire_Origin_Alarm_Type <- NULL
fire_data$Smoke_Alarm_Impact_on_Persons_Evacuating_Impact_on_Evacuation <- NULL
fire_data$Smoke_Spread <- NULL
fire_data$Sprinkler_System_Operation <- NULL
fire_data$Sprinkler_System_Presence <- NULL
fire_data$Status_of_Fire_On_Arrival <- NULL
fire_data$TFS_Firefighter_Casualties <- NULL
```

Compute two "new" variables to study; the time to arrival and the response (time to control the fire)
```{r, echo=F}
fire_data$TFS_Alarm_Time <- as.POSIXct(gsub("T", " ", fire_data$TFS_Alarm_Time), format="%Y-%m-%d %H:%M:%S", tz="UTC")
fire_data$TFS_Arrival_Time <- as.POSIXct(gsub("T", " ", fire_data$TFS_Arrival_Time), format="%Y-%m-%d %H:%M:%S", tz="UTC")
fire_data$Fire_Under_Control_Time <- as.POSIXct(gsub("T", " ", fire_data$Fire_Under_Control_Time), format="%Y-%m-%d %H:%M:%S", tz="UTC")
fire_data$Time_to_Arrival <- fire_data$TFS_Arrival_Time - fire_data$TFS_Alarm_Time
fire_data$Time_to_Undercontrol <- fire_data$Fire_Under_Control_Time - fire_data$TFS_Arrival_Time
```

Identify and remove missing data
```{r, echo=F}
missing_row = c()
for (column in fire_data) {
  which_missing <- which(is.na(column))
  missing_row <- append(missing_row, which_missing)
}

which_empty <- which(fire_data$Fire_Alarm_System_Operation == "")
missing_row <- append(missing_row, which_empty)

which_empty <- which(fire_data$Extent_Of_Fire == "")
missing_row <- append(missing_row, which_empty)

which_empty <- which(fire_data$Ignition_Source == "")
missing_row <- append(missing_row, which_empty)

unique_value <- unique(missing_row)
fire_data <- fire_data[-unique_value,]
```

Convert the "time to arrival" and "time to control" to numerical value
```{r, echo=F}
fire_data$Time_to_Arrival <- as.numeric(fire_data$Time_to_Arrival)
fire_data$Time_to_Undercontrol <- as.numeric(fire_data$Time_to_Undercontrol)
fire_data$Fire_Alarm_System_Operation <- as.numeric(sub("\\-.*", "", fire_data$Fire_Alarm_System_Operation))
fire_data$Extent_Of_Fire <- as.numeric(sub("\\-.*", "", fire_data$Extent_Of_Fire))
fire_data$Ignition_Source <- as.numeric(sub("\\-.*", "", fire_data$Ignition_Source))
```

Remove nonsensical values
```{r, echo=F}
which_nonsensical <- which(fire_data$Time_to_Arrival <= 1)
if (!length(which_nonsensical) == 0){
  fire_data <- fire_data[-which_nonsensical,]
}

which_nonsensical <- which(fire_data$Time_to_Undercontrol <= 1)
if (!length(which_nonsensical) == 0){
  fire_data <- fire_data[-which_nonsensical,]
}

fire_data$Number_of_responding_personnel <- as.numeric(fire_data$Number_of_responding_personnel)
which_nonsensical <- which(fire_data$Number_of_responding_personnel < 1)
if (!length(which_nonsensical) == 0){
  fire_data <- fire_data[-which_nonsensical,]
}
```

Remove undetermined values
```{r, echo=F}
fire_data <- fire_data[!fire_data$Fire_Alarm_System_Operation == 9, ]

fire_data <- fire_data[!fire_data$Extent_Of_Fire == 99, ]

fire_data <- fire_data[!fire_data$Ignition_Source == 999, ]
fire_data <- fire_data[!fire_data$Ignition_Source == 9990, ]
```

Split the data into training and test
```{r, echo=F}
nrow <- nrow(fire_data)
 
set.seed(7)    

?sample
s <- sample(1:nrow, nrow/2, replace=F)

train <- fire_data[s, ]

test <- fire_data[-s,]

write.csv(train, file="train_fire_data.csv")
write.csv(train, file="test_fire_data.csv")
```

Make sure the training and test dataset have similar statistics 
```{r, echo=F}
means_train <- apply(train[,c(6, 9, 10)], 2, mean)
means_test <- apply(test[,c(6, 9, 10)], 2, mean)

sds_train <- apply(train[,c(6, 9, 10)], 2, sd)
sds_test <- apply(test[,c(6, 9, 10)], 2, sd)

counts_extent_train <- as.numeric(table(train[,2]))
counts_extent_test <- as.numeric(table(test[,2]))

counts_alarm_train <- as.numeric(table(train[,3]))
counts_alarm_test <- as.numeric(table(test[,3]))

counts_ignition_train <- as.numeric(table(train[,5]))
counts_ignition_test <- as.numeric(table(test[,5]))
```

Variable | Training Set | Test Set
---------|--------------|--------------
Number of firefighters | `r means_train[1] ` (`r sds_train[1]`) | `r means_test[1]` (`r sds_test[1]`)
Time to arrival | `r means_train[2]` (`r sds_train[2]`) | `r means_test[2]` (`r sds_test[2]`)
Time to control the fire | `r means_train[3]` (`r sds_train[3]`)| `r means_test[3]` (`r sds_test[3]`)
Extent of the fire | `r counts_extent_train` | `r counts_extent_test`
Presence of fire alarm system | `r counts_alarm_train` | `r counts_alarm_test`
Ignition source | `r counts_ignition_train` | `r counts_ignition_test`

Table: The values in the "Time to arrival" row, the "Time to control the fire" row and the "Extent of the fire" row represent the mean and the value in parentheses is the standard deviation. The values in the "Extent of the fire" row, the  "Presence of fire alarm system" row and the "Ignition source" row represent the counts for each category.

EDA
```{r, echo=F}
pairs(train[,-c(1, 4, 7, 8)])
```

Fit a linear model
```{r, echo=F}
complete_model <- lm(Time_to_Undercontrol ~ Number_of_responding_personnel + Time_to_Arrival + as.factor(Extent_Of_Fire) + as.factor(Fire_Alarm_System_Operation) + as.factor(Ignition_Source), data=train)
```

Check additional assumptions
```{r, echo=F, eval=F}
# check condition 1
fit <- complete_model$fitted.values
plot(train$Time_to_Undercontrol ~ fit)
abline(a = 0, b = 1)
lines(lowess(train$Time_to_Undercontrol ~ fit), lty=2)

# check condition 2
pairs(train[,-c(1, 4, 7, 8, 10)])
par(mfrow=c(2,2))
```

Check assumptions for linear regression using the residuals
```{r, echo=F}
attributes(complete_model)
r <- complete_model$residuals
fit <- complete_model$fitted.values

par(mfrow=c(2, 2))
# create the residual versus fitted value plot
plot(r ~ fit, xlab="Fitted Values", ylab="Residuals")

# create each residual versus predictor plot
plot(r ~ train$Time_to_Arrival, xlab="Time to Arrival", ylab="Residuals")
plot(r ~ train$Number_of_responding_personnel, xlab="Number of Responding Personnel", ylab="Residuals")
plot(r ~ train$Fire_Alarm_System_Operation, xlab="Presence of Fire Alarm System", ylab="Residuals")
plot(r ~ train$Extent_Of_Fire, xlab="Extent of Fire", ylab="Residuals")
plot(r ~ train$Ignition_Source, xlab="Ignition Source", ylab="Residuals")

# create the qq plot
qqnorm(r, ylab = "Residuals Quantiles")
qqline(r)
```

Use BoxCox to help find a transformation
```{r, echo=F}
library(car)
boxCox(complete_model)
```

Fit new model
```{r, echo=F}
train$sqrtTime_to_Undercontrol <- sqrt(train$Time_to_Undercontrol)

transformed_model <- lm(sqrtTime_to_Undercontrol ~ Number_of_responding_personnel + Time_to_Arrival + as.factor(Extent_Of_Fire) + as.factor(Fire_Alarm_System_Operation) + as.factor(Ignition_Source), data=train)
```

Check condition 1 and 2 for transformed model
```{r, echo=F, eval=F}
# check condition 1
fit <- transformed_model$fitted.values
plot(train$sqrtTime_to_Undercontrol ~ fit)
abline(a = 0, b = 1)
lines(lowess(train$sqrtTime_to_Undercontrol ~ fit), lty=2)


# check condition 2
pairs(train[,-c(1, 4, 7, 8, 10)])
```

Check our assumptions using the residuals for the transformed model
```{r, echo=F}
attributes(transformed_model)
r <- transformed_model$residuals
fit <- transformed_model$fitted.values

par(mfrow=c(2,2))

# create the residual versus fitted values plot
plot(r ~ fit, xlab="Fitted Values", ylab="Residuals")

# create each residual versus predictor plot
plot(r ~ train$Time_to_Arrival, xlab="Time to Arrival", ylab="Residuals")
plot(r ~ train$Number_of_responding_personnel, xlab="Number of Responding Personnel", ylab="Residuals")
plot(r ~ train$Fire_Alarm_System_Operation, xlab="Presence of Fire Alarm System", ylab="Residuals")
plot(r ~ train$Extent_Of_Fire, xlab="Extent of Fire", ylab="Residuals")
plot(r ~ train$Ignition_Source, xlab="Ignition Source", ylab="Residuals")

# create the qq plot
qqnorm(r, ylab = "Residuals Quantiles")
qqline(r)
```

Fit reduced model
```{r, echo=F}
reduced_model_1 <- lm(sqrtTime_to_Undercontrol ~ Number_of_responding_personnel + as.factor(Fire_Alarm_System_Operation)  + as.factor(Extent_Of_Fire) + as.factor(Ignition_Source), data=train)
```

Check condition 1 and 2
```{r, echo=F, eval=F}
# check condition 1
fit_1 <- reduced_model_1$fitted.values
plot(train$sqrtTime_to_Undercontrol ~ fit_1)
abline(a = 0, b = 1)
lines(lowess(train$sqrtTime_to_Undercontrol ~ fit_1), lty=2)


# check condition 2
pairs(train[,-c(1, 4, 7:10)])
```

Check our assumptions using the residuals for the reduced model
```{r, echo=F}
attributes(reduced_model_1)
r_1 <- reduced_model_1$residuals
fit_1 <- reduced_model_1$fitted.values

par(mfrow=c(2,2))
# create the residual versus fitted value plot
plot(r_1 ~ fit_1, main="Residuals vs Fitted Values", xlab="Fitted Values", ylab="Residuals")

# create each residual versus predictor plot
plot(r_1 ~ train$Number_of_responding_personnel)
plot(r_1 ~ train$Fire_Alarm_System_Operation)
plot(r_1 ~ train$Extent_Of_Fire)
plot(r_1 ~ train$Ignition_Source)

# create the qq plot
qqnorm(r_1)
qqline(r_1)
```

Look for the leverage, outlier and influential points
```{r, echo=F, eval=F}
# values to use in cutoffs
n <- nrow(train)
p <- length(coef(reduced_model_1))-1

# define the cutoffs we will use
Hcut <- 2*((p+1)/n)
DFFITScut <- 2*sqrt((p+1)/n)
DFBETAcut <- 2/sqrt(n)
Dcut <- qf(0.5, p+1, n-p-1)

# identify the leverage points
h <- hatvalues(reduced_model_1)
which(h>Hcut)

# identify the outliers
r <- rstandard(reduced_model_1)
which(r < -4 | r > 4)

# identify influential points by Cook's distance
D <- cooks.distance(reduced_model_1)
which(D > Dcut)

# identify influential points by DFFITS
fits <- dffits(reduced_model_1)
which(abs(fits) > DFFITScut)

# identify influential points by DFBETAS
betas <- dfbetas(reduced_model_1)
dim(betas)

for(i in 1:91){
  print(paste0("Beta ", i-1))
  print(which(abs(betas[,i]) > DFBETAcut))
}

```

Remove non-sensical values
```{r, echo=F}
train <- train[!train$Time_to_Arrival > 15000, ]
```
For this point, the alarm time is 7am and the firefighters arrived at 11:57am, then took them 6 minutes to control the fire. This data largely deviate from the rest of the data and clearly appear to be a mistake. It does not make sense for firefighters to take almost 5hours to get to the area and extinguish the fire in 6 minutes.

```{r, echo=F}
train <- train[!train$sqrtTime_to_Undercontrol > 150, ]
```
The time was not properly recorded in this point which yield a high time to control the fire

```{r, echo=F}
train <- train[!train$Number_of_responding_personnel > 500, ]
```
This point does make some sense

Fit the new reduced model
```{r, echo=F}
reduced_model_2 <- lm(sqrtTime_to_Undercontrol ~ Number_of_responding_personnel + as.factor(Fire_Alarm_System_Operation) + as.factor(Extent_Of_Fire) + as.factor(Ignition_Source), data=train)
```

Check additional conditions
```{r, echo=F, eval=F}
# check condition 1
fit_2 <- reduced_model_2$fitted.values
plot(train$sqrtTime_to_Undercontrol ~ fit_2)
abline(a = 0, b = 1)
lines(lowess(train$sqrtTime_to_Undercontrol ~ fit_2), lty=2)


# check condition 2
pairs(train[,-c(1, 4, 7:10)])
```

Check our assumptions using the residuals for the final model
```{r, echo=F}
attributes(reduced_model_2)
r_2 <- reduced_model_2$residuals
fit_2 <- reduced_model_2$fitted.values

par(mfrow=c(2,2))
# create the residual versus fitted values plot
plot(r_2 ~ fit_2, xlab="Fitted Values", ylab="Residuals")

# create each residual versus predictor plot
plot(r_2 ~ train$Number_of_responding_personnel, xlab="Number of Responding Personnel", ylab="Residuals")
plot(r_2 ~ train$Fire_Alarm_System_Operation, xlab="Presence of Fire Alarm System", ylab="Residuals")
plot(r_2 ~ train$Extent_Of_Fire, xlab="Extent of Fire", ylab="Residuals")
plot(r_2 ~ train$Ignition_Source, xlab="Ignition Source", ylab="Residuals")

# create the qq plot
qqnorm(r_2)
qqline(r_2)
```

Check for multicolinearity
```{r, echo=F}
vif(reduced_model_2)
```

Compare between models
```{r, echo=F}
select = function(model, n)
{
  SSres <- sum(model$residuals^2)
  Rsq <- summary(model)$r.squared
  Rsq_adj <- summary(model)$adj.r.squared
  p <- length(model$coefficients) - 1
  AIC <- n*log(SSres/n) + 2*p     
  AICc <- AIC + (2*(p+2)*(p+3)/(n-p-1))
  BIC <- n*log(SSres/n) + (p+2)*log(n)    
  res <- c(SSres, Rsq, Rsq_adj, AIC, AICc, BIC)
  names(res) <- c("SSres", "Rsq", "Rsq_adj", "AIC", "AIC_c", "BIC")
  return(res)
}

# apply to the models
m1 <- select(complete_model, nrow(train))
m2 <- select(transformed_model, nrow(train))
f <- select(reduced_model_2, nrow(train))
```
Model | Adjusted $R^2$ | Corrected AIC | BIC 
------|----------------|-----|-----
Full model | `r round(m1[3], 2)` | `r m1[5]` | `r m1[6]`
Transformed model | `r m2[3]` | `r m2[5]` | `r m2[6]`
Reduced model | `r f[3]` | `r f[5]` | `r f[6]`

Table: Comparison between the different fitted models so that we can chose the preferred model. We chose the corrected AIC because the sampple size over the number of predictors plus two is smaller than 40.

Validation step
```{r, echo=F}
model_test <- lm(Time_to_Undercontrol ~ Number_of_responding_personnel + Time_to_Arrival + as.factor(Extent_Of_Fire) + as.factor(Fire_Alarm_System_Operation) + as.factor(Ignition_Source), data=test)
```

Check additional conditions
```{r, echo=F}
# check condition 1
fit_t <- model_test$fitted.values
plot(test$Time_to_Undercontrol ~ fit_t)
abline(a = 0, b = 1)
lines(lowess(test$Time_to_Undercontrol ~ fit_t), lty=2)


# check condition 2
pairs(test[,-c(1, 4, 7:8)])
```

Check our assumptions using the residuals for the test model
```{r, echo=F}
attributes(model_test)
r_t <- model_test$residuals
fit_t <- model_test$fitted.values

par(mfrow=c(2,2))
# create the residual versus fitted values plot
plot(r_t ~ fit_t, xlab="Fitted Values", ylab="Residuals")

# create each residual versus predictor plot
plot(r_t ~ test$Number_of_responding_personnel, xlab="Number of Responding Personnel", ylab="Residuals")
plot(r_t ~ test$Fire_Alarm_System_Operation, xlab="Presence of Fire Alarm System", ylab="Residuals")
plot(r_t ~ test$Extent_Of_Fire, xlab="Extent of Fire", ylab="Residuals")
plot(r_t ~ test$Ignition_Source, xlab="Ignition Source", ylab="Residuals")

# create the qq plot
qqnorm(r_t)
qqline(r_t)
```

```{r, echo=F}
test$sqrtTime_to_Undercontrol <- sqrt(test$Time_to_Undercontrol)

reduced_model_test <- lm(sqrtTime_to_Undercontrol ~ Number_of_responding_personnel + as.factor(Fire_Alarm_System_Operation)  + as.factor(Extent_Of_Fire) + as.factor(Ignition_Source), data=test)
```

Check additional conditions
```{r, echo=F}
# check condition 1
fit_t <- reduced_model_test$fitted.values
plot(test$sqrtTime_to_Undercontrol ~ fit_t)
abline(a = 0, b = 1)
lines(lowess(test$sqrtTime_to_Undercontrol ~ fit_t), lty=2)


# check condition 2
pairs(test[,-c(1, 4, 7:10)])
```

Check our assumptions using the residuals for the reduced model
```{r, echo=F}
attributes(reduced_model_test)
r_t <- reduced_model_test$residuals
fit_t <- reduced_model_test$fitted.values

par(mfrow=c(2,2))
# create the residual versus fitted values plot
plot(r_t ~ fit_t, xlab="Fitted Values", ylab="Residuals")

# create each residual versus predictor plot
plot(r_t ~ test$Number_of_responding_personnel, xlab="Number of Responding Personnel", ylab="Residuals")
plot(r_t ~ test$Fire_Alarm_System_Operation, xlab="Presence of Fire Alarm System", ylab="Residuals")
plot(r_t ~ test$Extent_Of_Fire, xlab="Extent of Fire", ylab="Residuals")
plot(r_t ~ test$Ignition_Source, xlab="Ignition Source", ylab="Residuals")

# create the qq plot
qqnorm(r_t)
qqline(r_t)
```

\pagebreak
```{r, echo=F}
p1 <- length(coef(reduced_model_2))-1
n1 <- nrow(train)
vif1 <- max(vif(reduced_model_2))
D1 <- length(which(cooks.distance(reduced_model_2) > qf(0.5, p1+1, n1-p1-1)))
fits1 <- length(which(abs(dffits(reduced_model_2)) > 2*sqrt((p1+1)/n1)))

coefs1 <- round(summary(reduced_model_2)$coefficients[,1], 3)
ses1 <- round(summary(reduced_model_2)$coefficients[,2], 3)

tp1 <- length(coef(reduced_model_test))-1
tn1 <- nrow(test)
tvif1 <- max(vif(reduced_model_test))
tD1 <- length(which(cooks.distance(reduced_model_test) > qf(0.5, tp1+1, tn1-tp1-1)))
tfits1 <- length(which(abs(dffits(reduced_model_test)) > 2*sqrt((tp1+1)/tn1)))

tcoefs1 <- round(summary(reduced_model_test)$coefficients[,1], 3)
tses1 <- round(summary(reduced_model_test)$coefficients[,2], 3)

vif(reduced_model_2)
vif(reduced_model_test)
```

Characteristic | Preferred Model (Train) | Preferred Model (Test) 
---------------|----------------|---------------
R-squared | 0.3831 | 0.3858 
Adjusted R-squared | 0.3662 | 0.3695 
---------------|----------------|---------------
Largest VIF value | 1.45 | 1.35 
Number of Cook's D | `r D1` | `r tD1` 
Number of DFFITS | `r fits1` | `r tfits1` 
Violations | Constant variance, Normality | Constant variance, Normality  
---------------|----------------|---------------
Intercept | `r coefs1[1]` $\pm$ `r ses1[1]`  | `r tcoefs1[1]` $\pm$ `r tses1[1]`  
Number_of_responding_personnel   | `r coefs1[2]` $\pm$ `r ses1[2]`  |`r tcoefs1[2]` $\pm$ `r tses1[2]` 
Fire_Alarm_System_Operation-2  | `r coefs1[3]` $\pm$ `r ses1[3]` |`r tcoefs1[3]` $\pm$ `r tses1[3]` 
Fire_Alarm_System_Operation-8 | `r coefs1[4]` $\pm$ `r ses1[4]`  | `r tcoefs1[4]` $\pm$ `r tses1[4]`
Extent_Of_Fire-2  | `r coefs1[5]` $\pm$ `r ses1[5]`  | `r tcoefs1[5]` $\pm$ `r tses1[5]` 
Extent_Of_Fire-3  |  `r coefs1[6]` $\pm$ `r ses1[6]`  | `r tcoefs1[6]` $\pm$ `r tses1[6]` 
Extent_Of_Fire-4  |  `r coefs1[7]` $\pm$ `r ses1[7]`   | `r tcoefs1[7]` $\pm$ `r tses1[7]`
Extent_Of_Fire-5  | `r coefs1[8]` $\pm$ `r ses1[8]`  | `r tcoefs1[8]` $\pm$ `r tses1[8]` 
Extent_Of_Fire-6 | `r coefs1[9]` $\pm$ `r ses1[9]`   | `r tcoefs1[9]` $\pm$ `r tses1[9]`
Extent_Of_Fire-7  | `r coefs1[10]` $\pm$ `r ses1[10]`   | `r tcoefs1[10]` $\pm$ `r tses1[10]`
Extent_Of_Fire-8 |  `r coefs1[11]` $\pm$ `r ses1[11]`   | `r tcoefs1[11]` $\pm$ `r tses1[11]`
Extent_Of_Fire-9 |  `r coefs1[12]` $\pm$ `r ses1[12]`   | `r tcoefs1[12]` $\pm$ `r tses1[12]`
Extent_Of_Fire-10  |  `r coefs1[13]` $\pm$ `r ses1[13]`   | `r tcoefs1[13]` $\pm$ `r tses1[13]` 
Extent_Of_Fire-11  |  `r coefs1[14]` $\pm$ `r ses1[14]`   | `r tcoefs1[14]` $\pm$ `r tses1[14]`
Ignition_Source-12 | `r coefs1[15]` $\pm$ `r ses1[15]`   | `r tcoefs1[15]` $\pm$ `r tses1[15]` 
Ignition_Source-13 | `r coefs1[16]` $\pm$ `r ses1[16]`   | `r tcoefs1[16]` $\pm$ `r tses1[16]`   
Ignition_Source-14  | `r coefs1[17]` $\pm$ `r ses1[17]`   | `r tcoefs1[17]` $\pm$ `r tses1[17]`   
Ignition_Source-15  | `r coefs1[18]` $\pm$ `r ses1[18]`   | `r tcoefs1[18]` $\pm$ `r tses1[18]`
Ignition_Source-16  | `r coefs1[19]` $\pm$ `r ses1[19]`   | `r tcoefs1[19]` $\pm$ `r tses1[19]`
Ignition_Source-17  | `r coefs1[20]` $\pm$ `r ses1[20]`   | `r tcoefs1[20]` $\pm$ `r tses1[20]`
Ignition_Source-19  | `r coefs1[21]` $\pm$ `r ses1[21]`   | `r tcoefs1[21]` $\pm$ `r tses1[21]` 
... | ... | ...

Table: Comparisons between the preferred model on the train and test data. For each coefficient, the first value is the mean and the second value is the standard deviation.
